%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Lead Front-End Engineer (Angular, Ionic)} % Job title
    {Shoop Germany GmbH} % Organization
    {Berlin, Germany} % Location
    {Aug. 2020 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Lead development of Admin Panel and Support Tickets System.}
        \item {Implemented a number of key features like Two-Factor-Auth, Infinity Scroll, Onboarding Flow.}
        \item {Increased E2E and Unit tests coverage by 25\%.}
        \item {Migrated projects to the TypeScript strict mode, that improved Developer Experience, and the project’s overall reliability.}
        \item {Refactored core functionality of a project. Within the refactoring solved multiple problems related to memory leaking, rendering optimization, and performance issues.}
        \item {On-boarded and coached new team members.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Senior Front-End Engineer \& Report Writing Expert (ReactJS, EmberJS)} % Job title
    {Shiji Deutschland GmbH} % Organization
    {Berlin, Germany} % Location
    {May. 2018 - Aug. 2020} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed architecture and implemented two Micro Front-End modules from scratch.}
        \item {Created multiple components for the project's components base.}
        \item {Implemented and optimized Analytics Dashboard UI to display a big amount of live data.}
        \item {Conducted many workshops for classes with 20+ people.}
        \item {Wrote 30+ Analytics Report Templates using Stimulsoft Report Engine and PostgreSQL.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Front-End Engineer (Angular)} % Job title
    {Skynix LLC} % Organization
    {Kyiv, Ukraine} % Location
    {Oct. 2017 - May. 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed 70+ screens using Angular and Ionic.}
        \item {Setup SSR for Angular applications to solve SEO issues.}
        \item {Designed complex JavaScript and CSS animations and transitions.}
        \item {Wrote multiple technical articles for the corporate blog.}
        \item {On-boarded and coached new team members.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Front-End Engineer} % Job title
    {ModXart Web Studio} % Organization
    {Kyiv, Ukraine} % Location
    {Dec. 2016 - Oct. 2017} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Designed 5 SPA applications from scratch using ReactJS and Angular.}
        \item {Developed multiple screens and widgets for the online payment system.}
        \item {Did SEO and performance optimization.}
        \item {Developed Telegram bots using Telegram Javascript SDK.}
        \item {Did applications performance audit.}
      \end{cvitems}
    }
\end{cventries}
