%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Lead Frontend Engineer} % Job title
    {Shoop Germany GmbH} % Organization
    {Berlin, Germany} % Location
    {Aug. 2020 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Implement complex features as Two-Factor-Auth, Onboarding Flow, Support Ticket System.}
        \item {Increased E2E and Unit tests coverage by 25\%.}
        \item {Migrated apps to the strict mode, that improved DX and project’s overall reliability.}
        \item {Participated in constant project’s architecture refactoring.}
        \item {Responsible for making releases, including App Store and Google Play.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Senior Front-End Engineer} % Job title
    {Shiji Deutschland GmbH} % Organization
    {Berlin, Germany} % Location
    {May. 2018 - Aug. 2020} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed an architecture, initiated and maintained dedicated Micro Front-End Module.}
        \item {Conducted many workshops and onboarding sessions.}
        \item {Maintained project’s web-components base.}
        \item {Closely collaborated with other teams, participated in app’s architecture decision making.}
        \item {Analytics Report Writing using Stimulsoft Report Engine and PostgreSQL.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Front-End Engineer} % Job title
    {Skynix LLC} % Organization
    {Kyiv, Ukraine} % Location
    {Oct. 2017 - May. 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed and maintained many SPA projects from scratch.}
        \item {SPA performance optimization.}
        \item {Designed complex JavaScript animations.}
        \item {Wrote technical articles for the corporate blog.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Front-End Engineer} % Job title
    {ModXart} % Organization
    {Kyiv, Ukraine} % Location
    {Dec. 2016 - Oct. 2017} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Designed UI plugins.}
        \item {Optimized websites performance.}
        \item {Designed various messenger bots.}
      \end{cvitems}
    }
\end{cventries}
